---
title: "Sentiment of ZEIT ONLINE articles"
author: "Jan Dix"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sentiment of ZEIT ONLINE articles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this vignette we will use `rzeit2` to download meta data about articles on ****

"Opinion mining (sometimes known as sentiment analysis or emotion AI) refers to the use of natural language processing, text analysis, computational linguistics, and biometrics to systematically identify, extract, quantify, and study affective states and subjective information." (Wikipedia, 2018)

```{r}
library(rzeit2)
library(robotstxt)
```


### Download the meta data

```{r get meta data}
# download the meta data
meta <- get_content("Merkel",
                    limit = 200,
                    sort="release_date desc")
# extract actual content
meta_df <- meta$content
```

### Scrape the articles

```{r robotstxt}
robotstxt <- robotstxt("https://zeit.de")
robotstxt$permissions
```


```{r scrape articles}
articles <- get_article_text(meta_df$href, timeout = 1)
```


### Calculate the sentiment

In our example we will use a dictionary approach. 

### Plot the sentiment by day



